---
title: "Final Project Proposal"
output:
  pdf_document: default
  html_document: default
Author: Grace Jennings, Nathaniel Hartley, Kartik Chamarti
---

### Plastic Pollution in the US

```{r import}
library(tidyverse)
plastics <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-01-26/plastics.csv')
```
### Data
```{r data}
glimpse(plastics)
```
### Research Question

As a result of climate change and the increasing human impact on our 
environment, it is important to look at the trends of pollution from 
corporations as they do have a large impact on the environment relative
to individual human beings. I hope to answer two research questions. I hope
to explore which category of plastic contributes most to pollution around
the world. I also hope to see whether there was a change in plastic pollution
from 2019 and 2020. It would also be interesting to see which company 
contributes the most to plastic pollution. 

The null hypothesis is that there is no change in plastic pollution between 2019
and 2020. The alternate hypothesis is that there is a change in plastic 
pollution between 2019 and 2020. For my other research question, on which 
category of plastic contributes the most to pollution, more analysis would
need to be done to have an idea of it. However, I believe that the
polystyrene (ps) count would contribute most to pollution because its
substituents such as toys, cups, and styrofoam is very popular among human use.

Note: Since I used a link to load the data, I am unable to use the data folder.
Rather, the data folder has a part of my larger dataset. 

